Turbulence in compact to giant HII regions

### 2021-10-01 strucfunc_paper.tex
Javier changes 2021-09-30
Progress on the caption to Fig 1

\newcommand\ha{\ensuremath{\text{H}\alpha}}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{Figures/hii-region-mosaic}
  \caption{The sample of nine \hii{} regions used in this study.}
  \label{fig:hii-regions}
\end{figure*}

@@

\begin{figure*}
\centering
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/604}\par
\includegraphics[width=1.5in]{Figures/Hist/595}\par
\includegraphics[width=1.5in]{Figures/Hist/346}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/Hubble-V}\par
\includegraphics[width=1.5in]{Figures/Hist/Hubble-X}\par
\includegraphics[width=1.5in]{Figures/Hist/30Dor}\par
\end{multicols}
\begin{multicols}{3}
\includegraphics[width=1.5in]{Figures/Hist/M8}\par
\includegraphics[width=1.5in]{Figures/Hist/Car}\par
\includegraphics[width=1.5in]{Figures/Hist/OrionS}\par
\end{multicols}
\caption{Histograms of the centroid velocities of our sample of HII regions. }
\label{fig:hist}
\end{figure*}

>>>>

\newcommand\ha{\ensuremath{\text{H}\alpha}}
\newcommand\Wav[1]{\ensuremath{\lambda #1}}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{Figures/hii-region-mosaic}
  \caption{
    The sample of nine \hii{} regions employed in this study,
    arranged from top to bottom in order of distance.
    White shapes show the approximate extents of the
    emission line maps that we use for studying the ionized gas kinematics.
    Scale bars show the equivalent linear length scales at the distance to each region.
    For Orion, two fields are shown: the Extended Orion Nebula,
    sampled at a scale of \SI{0.1}{pc}, and the central Huygens region,
    sampled at a scale of \SI{0.004}{pc}.
    All images are combinations of optical narrow-band and wide-band filters.
    In most cases, red/orange/pink represents \ha{} or other emission lines
    emitted by the ionized gas,
    while blue/white represents continuum starlight from young high-mass stars.
    In some cases, green (for Hubble~X and NGC~604) or blue (for NGC~595)
    represents the [\ion{O}{3}] \Wav{5007} emission line.
    Image credits as follows.
    Orion Nebula:
    \textit{HST} Treasury Program on the Orion Nebula Cluster \citep{Robberto:2013a}.
    M8 Lagoon: R. Jay Gabany (\url{https://www.cosmotography.com/index.html}).
    Carina: ESO/Digitized Sky Survey~2, Davide De Martin
    (\url{https://www.eso.org/public/images/eso0905b})
    NGC~346: NASA, ESA and A. Nota (ESA/STScI) \citep{Nota:2006x}.
    30 Doradus: Robert Gendler, Roberto Colombari,
    Hubble Legacy Archive, European Southern Observatories
    (\url{http://www.robgendlerastropics.com/Tarantula-HST-ESO.html}).
    Hubble~X:
    Hubble~V:
    NGC~595:
    NGC~604:
  }
  \label{fig:hii-regions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=5in]{Figures/Hist/Hist}\par
\caption{Histograms of the centroid velocities of our sample of HII regions. }
\label{fig:hist}
\end{figure*}
